---
title: "Principle Component Aanalysis"
output: html_document
---
#Data
The data you will be using comes from teh Assistments online intelligent tutoring system (https://www.assistments.org/). It describes students working through online math problems. Each student has the following data associated with them:

- id
- prior_prob_count: How many problems a student has answered in the system prior to this session
- prior_percent_correct: The percentage of problems a student has answered correctly prior to this session
- problems_attempted: The number of problems the student has attempted in the current session
- mean_correct: The average number of correct answers a student made on their first attempt at problems in the current session
- mean_hint: The average number of hints a student asked for in the current session
- mean_attempt: The average number of attempts a student took to answer a problem in the current session
- mean_confidence: The average confidence each student has in their ability to answer the problems in the current session

#Start by uploading the data
```{r}
D1 <- 

  #We won't need to id variable, so remove that.


```

#Create a correlation matrix of the relationships between the variables, including correlation coefficients for each pair of variables/features.

```{r}
#You can install the corrplot package to plot some pretty correlation matrices (sometimes called correlograms)

library(corrplot)

#Generate pairwise correlations
COR <- cor(D1)

corrplot(COR, order="AOE", method="circle", tl.pos="lt", type="upper",        
tl.col="black", tl.cex=0.6, tl.srt=45, 
        addCoef.col="black", addCoefasPercent = TRUE,
        sig.level=0.50, insig = "blank")

#Study your correlogram image and save it, you will need it later
```

#Create a new data frame with the mean_correct variables removed

```{r}
D2 <- 

#The, scale and center your data for easier interpretation
D2 <- scale(D2, center = TRUE)
```

#Now run the PCA on the new data frame

```{r}
pca <- prcomp(D2, scale = TRUE)
```

#Although the algorithm does not generate the eigenvalues directly for us, we can print a list of the standard deviation of the variance accounted for by each component.

```{r}
pca$sdev

#To convert this into variance accounted for we can square it, these numbers are proportional to the eigenvalue

pca$sdev^2

#A summary of our pca will give us the proportion of variance accounted for by each component

summary(pca)

#We can lot this to get an idea of which components we should keep and which we should drop

plot(pca, type = "lines")
```

#Think about which components you would drop and make a decision

```{r}
#Now, create a data frame of the transformed data from your pca.

D3 <- as.data.frame(pca$x)

#Attach the variable "mean_correct" from your original data frame to D3.

D4 <- cbind(D3, as.data.frame(D1$mean_correct))

#Now re-run your scatterplots and correlations between the transformed data and mean_correct. If you had dropped some components would you have lost important infomation about mean_correct?

COR2 <- 

  
```

